### 2025-06-18 simulation.qmd
20250617 - fix duplicate chunk label
20250617 - reduce iterations to fix memory issue

bootstappedStats <- bootstrapSimulation(
  projectedStats = all_proj,
  vars_by_pos = vars_by_pos,
  n_iter = 10000,
  seed = 52242)
```

@@

bootstappedStats <- bootstrapSimulation(
  projectedStats = all_proj,
  vars_by_pos = vars_by_pos,
  n_iter = 10000,
  seed = 52242,
  progress = FALSE)
```

@@

>>>>

bootstappedStats <- bootstrapSimulation(
  projectedStats = all_proj,
  vars_by_pos = vars_by_pos,
  n_iter = 5000,
  seed = 52242)
```

@@

bootstappedStats <- bootstrapSimulation(
  projectedStats = all_proj,
  vars_by_pos = vars_by_pos,
  n_iter = 5000,
  seed = 52242,
  progress = FALSE)
```

@@

```{r}
#| label: put-simulated-data-in-format-for-scoring2
